Top Text

### 2022-12-05 Paper.tex
Update introduction and methods

	\section{Introduction}
During the year of 2022 there has been a massive increase in the popularity and use of text-to-image generators, an artificial intelligence technique that translates human text into a computer-generated image. This has led to many different generators being made, which on the one hand has given many more options to artists (people who use a text-to-image generator to create and refine an image), but it has also made the landscape difficult to navigate with its abundance of choice. These new options are great for the field as a whole, however it also means that artists who are not experienced may struggle to find the generator which suits their needs. This paper makes an effort to try and alleviate this problem by picking four of the most used text-to-image generators and comparing them based on their accuracy and process so we can help people gain some perspective on which text-to-image generator is best for their needs.

A research paper was published on the nineteenth of February 2020 called: "A survey and taxonomy of adversarial neural networks for text-to-image synthesis" that makes use of surveys to compare models for text-to-image generations. This paper aimed to show which text-to-image technique yielded the most realistic results in a wide variety of categories. One issue with this paper was that is was written before the explosion of consumer text-to-image generators happened, which is why we will instead focus on modern consumer-grade generators which are available today. Another issue is that they don't allow average people to use their tools. Instead their results are created by the researchers themselves, this causes the results to show the absolute best a text-to-image generator can create instead of what the average artist can expect.

Our goal during the course of this research paper is to find out what is the best text-to-image generator, out of the four we chose, for artists who are experienced as well as artists who are not experienced in artificial art generation. Our hope is that artists that are new to text-to-image generation will be able to make an educated decision on which generator is best for them on the basis of this paper.

Another question we take a look at is to find the best technique out of the four applications that we use and then analysing why that technique is so effective for artificial intelligence text-to-image generation. The techniques we will take a look at are latent diffusion, the V4 model, and VOGAN and CLIP.

@@

We expect the best text-to-image generator out of the four we chose to be stable diffusion. This is due to the fact that stable diffusion offers its users more tools and techniques like inpainting (allows you to regenerate a specific area of an image without regenerating the whole image), this allows the user more freedom to fine-tune their result. Given enough time this will yield a more accurate result. This however, only applies for artists who are already experienced, we expect inexperienced artists to struggle finding the right settings because of the amount of freedom they get. In the case of inexperienced artists, they might find DallE easier to use because it creates photo realistic results without having to fine tune any settings apart from their prompt.

@@

	A secondary research question that we take a look at in this paper is to find out the strengths of the different ai text to image generation techniques used in the applications we have chosen.

@@

	We have chosen an image that we find sufficiently covers all the hard parts of recreating an image using ai art generation such as reflections and complex composition. We then use each of the four artificial intelligence applications to try and recreate that image within a given time frame (30 minutes ) and after each iteration we take that image and compile it into a list of the iterations for the process of recreating that image for that specific application. With those sets of data, we then plug the images (each iteration) into an AI application that can give you a numerical value for how close one image is to another and see how close each iteration is to the image we are trying to recreate. this then gives us insight into how fast the application is (how efficient its technique is) and how many iterations you have to do to achieve a certain result. Once the data is gathered, we can create a graph to compare the applications more easily. The people that carried out this experiment also consisted of one novice and one experienced individual. This is to see which is the best application for each group of people and thus, the results will be conveyed on two separate graphs. In terms of our secondary research question this method also gives us insight if we are aware of the techniques each of them use we can notice if there is a pattern of success or failure with each.

>>>>

	\section{Introduction}
During the year of 2022 there has been a massive increase in the popularity and use of text-to-image generators, an artificial intelligence technique that translates human text into a computer-generated image. You will likely have heard of at least one of these if you frequent the internet. This explosion in popularity has led to many different text-to-image applications being made, which on the one hand has given many more options to artists, (people who use a text-to-image generator to create and refine an image), but it has also made the landscape more difficult to navigate because of its abundance of choice. This paper makes an effort to try and alleviate this problem by picking four of the most used text-to-image generators and comparing them based on their accuracy and process so we can help people gain some perspective on which text-to-image generator is best for their needs.

A research paper was published on the nineteenth of February 2020 called: "A survey and taxonomy of adversarial neural networks for text-to-image synthesis" that makes use of surveys to compare models for text-to-image generations. This paper aimed to show which text-to-image technique yielded the most realistic results in a wide variety of categories. One issue with this paper was that is was written before the explosion of consumer text-to-image generators happened, which is why we will instead focus on modern consumer-grade generators which are available today. Another issue is that they don't allow average inexperienced artists to use their tools, instead their results are created by the researchers themselves. Because of this their results do not reflect what the average inexperienced artist can expect when using these text-to-image techniques.

Our goal during the course of this research paper is to find out what the best text-to-image generator is, out of the four we chose, in the case of an artist who is not experienced in the world of text-to-image generation. Our hope is that artists that are new to text-to-image generation will be able to make an educated decision on which generator is best for them on the basis of this paper.

(? maybe instead focus on the tools inside the application.) Another question we take a look at is to find the best technique out of the four applications that we use and then analysing why that technique is so effective for artificial intelligence text-to-image generation. The techniques we will take a look at are latent diffusion, the V4 model, and VOGAN and CLIP.

@@

We expect the best text-to-image generator out of the four we chose to be stable diffusion. This is due to the fact that stable diffusion offers its users more tools and techniques like inpainting (allows you to regenerate a specific area of an image without regenerating the whole image), this allows the user more freedom to fine-tune their result. Given enough time this will yield a more accurate result. This however only applies for artists who are already experienced, because it can take quite some practice to get used to all the tools that are available in stable diffusion. We expect inexperienced artists to struggle finding the right settings because of the amount of freedom they get. In the case of a completely inexperienced artist, they might find Dall-E easier to use because it can create photorealistic results without having to fine tune any settings apart from the prompt.

@@

	(? Instead look at amount of tools available) A secondary research question that we take a look at in this paper is to find out the strengths of the different ai text to image generation techniques used in the applications we have chosen.

@@

	We have chosen an image that we find sufficiently covers all the hard parts of recreating an image using ai art generation such as reflections and complex composition. We then use each of the four artificial intelligence applications to try and recreate that image within a given time frame (15 minutes). After each iteration we take that image and compile it into a list of the iterations for the process of recreating that image for that specific application. With those sets of data, we then run the images (each iteration) through an AI application developed by DeepAI that can give you a numerical value (distance) based on how close one image is to another, the lower the distance the closer the image. This way we can see how close each iteration is to the image we are trying to recreate.

	Once the data is gathered, we can create a graph to compare the applications more easily. The people that carried out this experiment also consisted of one novice and one experienced individual. This is to see which is the best application for each group of people and thus, the results will be conveyed on two separate graphs.

	In terms of our secondary research question this method also gives us insight if we are aware of the techniques each of them use we can notice if there is a pattern of success or failure with each.
